Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-08-15 preamble.rnw
Add "S" to figure numbers in the supplementary.
Set up xr to link from the article to the supplementary.
Change the cleveref range conjuntion to an en-dash.
Load xr-hyper to fix the hyperlinks tothe supplementary.
Move code for the figures into the article-analysis script.
Remove unnecessary uses of the knitr namespace.
knitr is loaded in the Makefile,
so explicitly specifying the namespace is unnecessary.

%Images & tables
\usepackage{subcaption}
\usepackage{pgfplots}
\usepackage{colortbl}
\usepackage{multirow}
\usepackage{arydshln}

@@

@@

<<include=FALSE>>=
	knitr::opts_chunk$set(echo = FALSE) #Never show the code, only output.
	knitr::opts_chunk$set(results = 'asis') #Text is grey without this.
	knit_hooks$set(inline = function(x) {x}) #Disable automatic formatting of in-line material.
@

@@

\pgfplotsset{%
	colormap={coclassification}{color=(white) color=(red)}
}
\colorlet{coclassification diagonal}{black!20}

>>>>

%Images & tables
\usepackage{subcaption}
\usepackage{pgfplots}
\usepackage{colortbl}
\usepackage{multirow}
\usepackage{arydshln}
\usepackage{xr}
\usepackage{xr-hyper}

@@

\newcommand{\crefrangeconjunction}{--}

%Supplementary
\newcommand{\beginsupplementary}{%
	\setcounter{table}{0}
	\renewcommand{\thetable}{S\arabic{table}}%
	\setcounter{figure}{0}
	\renewcommand{\thefigure}{S\arabic{figure}}%
}

@@

<<include=FALSE>>=
	opts_chunk$set(echo = FALSE) #Never show the code, only output.
	opts_chunk$set(results = 'asis') #Text is grey without this.
	knit_hooks$set(inline = function(x) {x}) #Disable automatic formatting of in-line material.
@

@@

<<>>=
	cat(coclassification_colour_setup)
@
